Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
update section 7

In previous section, we presented a refunctionalized AAM that in extended continuation-passing style.
To obtain a definitional abstract interpreter, we need to transform it further to direct-style.
At this point, we have two choices:
1) By monadifying the continuations into monads, we obtain the \citeauthor{darais2017abstracting}'s
abstracting definitional interpreter in monadic style.
2) By representing the extended continuation-passing style with delimited continuations,
we derive a new form of abstract interpreters in direct-style.
This coincidence should not be a surprise since there are extraordinarily rich literatures
show the correspondence between monads and continuations as of their very beginning era
(TODO: cite Danvy/abs control/esce of fp).
In fact, we can also just use the same caching algorithm but with side effect such as
assignments and mutations to achieve the same definitional interpreter with pushdown
control flows.
In this section, we present both of versions using monads and delimited controls.

\subsection{Monadification} \label{monadify}

In this section, we show how to transform the refunctionalized AAM to monadic-style
abstracting definitional interpreters.

\subsection{Un-CPS} \label{uncps}

>>>>

In previous section, we presented a refunctionalized AAM with @nd@ operator 
in extended continuation-passing style.
To obtain definitional abstract interpreters, we now transform it further to direct-style.

To do this at this point, we actually have multiple choices:
\begin{itemize}
  \item By monadifying the continuations into monads, we obtain the abstracting
    definitional interpreters in monadic style which are what \citeauthor{darais2017abstracting}
    described \cite{darais2017abstracting}.
  \item By representing the extended continuation-passing style with delimited controls,
    we derive a new form of abstract interpreters in direct-style.
  \item In fact, we may also just use the same caching algorithm but with side effect such as
    assignments and mutations to update the cache and then achieve the same 
    definitional interpreter with pushdown control flows. In this case, nondeterminism can be 
    well handled by for comprehension.
\end{itemize}

These coincidence should not be a surprise since there are extraordinarily rich literatures
show the correspondence between monads and continuation-passing style as well as delimited 
controls since their very beginning era. \todo{cite}

In this section, we present the version that using delimited controls.

\subsection{Un-CPS by Delimited Controls} \label{uncps}
